404 -- Page Not Found   

### 2025-08-29 LipidProbe/Phosphatidylethanolamine.qmd
Spent a long time learning about custom divs, applied a new one for cell types
Addressing more of the reviewer comments, accession numbers mostly

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

```{r setup, echo=FALSE, include=FALSE}

## intitialize libraries
library(here)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

```{r, echo=FALSE, include=FALSE}

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.

# Read the data to a df
data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(data))){
	ID[i] = i
}

# Applies the ID column to the PE results
AT_2025_ranked <- data |>
    arrange(logFC) |>
	filter(LipidProbe == "PE") |>
	mutate(ID = ID)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

RankedOrderPlotStandard(AT_2025_ranked)
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

print("Data not yet provided.")

```
:::
:::

#### Gene Ontology Analysis

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
::::
:::::

@@

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation,
                  inline="true")
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))
```
:::

{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download">}}

@@

>>>>

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
format: 
  html:
    embed-resources: false
---

@@

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

here()

## Opening the source file for the ggplot custom theme
source(here("Resources/ggplot_styles.R"))

# Read the membrane data to a df
data <- readr::read_csv(here("LipidProbe/DataSets/PE_membrane_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

RankedOrderPlotStandard(data)
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

MAStandard(data)

:::
::::
:::

<!-- 
#### Gene Ontology Analysis

@@

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
::::: -->

@@

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))

<br>

{{< downloadthis DataSets/PE_membrane_HeLa_AT_2025.csv dname="PE_membrane_HeLa_AT_ChemComm_download">}}

@@

:::{.cells collapse="true"}
::::{.cells-header}
Cytosolic Fraction
::::
::::{.cells-container}

```{r setup2, echo=FALSE, include=FALSE}

# Read the membrane data to a df
data <- readr::read_csv(here("LipidProbe/DataSets/PE_cytosol_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

RankedOrderPlotStandard(data)
```
:::

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd). MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

MAStandard(data)

:::
::::
:::

# Here is the code to make the filterable lists shown in the crosstalk table below
# Slight cleanup for presenting in the datatable
data <- data |>
  mutate(logFC = signif(logFC, digits=3)) |>
  mutate(pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation) |>
  select(-Protein.Description)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))

<br>

{{< downloadthis DataSets/PE_cytosol_HeLa_AT_2025.csv dname="PE_cytosol_HeLa_AT_ChemComm_download">}}

::::
:::

### 2025-08-29 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
Addressing more of the reviewer comments, accession numbers mostly

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

@@

RM_2021_data <- RM_2021_data |>
  select(-hit_annotation_method) |>
  mutate(
    logFC = signif(logFC, digits = 4),
    pvalue = signif(pvalue, digits = 4),
    AveExpr = signif(AveExpr, digits = 4),
    fdr = signif(fdr, digits = 4)
  )

@@

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 10))

>>>>

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(here)
here()
## Opening the source file for the ggplot custom theme
source((here("Resources/ggplot_styles.R")))

@@

RM_2021_data <- RM_2021_data |>
  select(-hit_annotation_method, -Protein.Description) |>
  mutate(
    logFC = signif(logFC, digits = 4),
    pvalue = signif(pvalue, digits = 4),
    AveExpr = signif(AveExpr, digits = 4),
    fdr = signif(fdr, digits = 4)
  )

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 10),
          colnames = c("Rank", "Gene Name", "Accession #","Lipid Probe", "Fraction", "LogFC", "p value", "FDR", "Hit Annotation"))

### 2025-08-29 LipidProbe/Sphinganine.qmd
Addressing more of the reviewer comments, accession numbers mostly

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

@@

# Opening the datatable for this page
data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "Spa")

@@

data <- data |>
  dplyr::select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation, -logFC)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))

```
:::

>>>>

## Opening the source file for the ggplot custom theme
source(here("Resources/ggplot_styles.R"))

@@

# Opening the datatable for this page
data <- readr::read_csv(here("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv"), ) |>
	filter(LipidProbe == "Spa")

@@

data <- data |>
  dplyr::select(gene_name, protein_id, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation, -logFC)

@@

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 10),
                         colnames = c("Rank", "Gene Name","Accession #", "Hit Annotation", "LogFC", "p value", "FDR"))

'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
:::

### 2025-08-29 LipidProbe/Sphingosine.qmd
Addressing more of the reviewer comments, accession numbers mostly

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))

>>>>

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 10),
                         colnames = c("Rank", "Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value", "FDR"))

```
'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
:::

### 2025-08-29 StudyInformation_includes/AT_2025_include.qmd
working on uploading Franks new analysis of Alixs data. Working in new branch.
Addressing more of the reviewer comments, accession numbers mostly

>>>>

Cell lysates were separated into membrane and cytosolic fractions. This publication reports the results of just the membrane fraction.

#### Data wrangling
Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:

{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_wrangling.R dname="AT_ChemComm2025_wrangling">}}

### 2025-08-29 StudyInformation_includes/DCC_2025_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

>>>>

#### Data wrangling
Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:

{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/DCC_2025_wrangling.R dname="DCC_2025_wrangling">}}

### 2025-08-29 StudyInformation_includes/RM_2021_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

>>>>

#### Data wrangling
Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:

{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/RM_2021_Wrangling.R dname="RM_2021_wrangling">}}

### 2025-08-29 StudyInformation_includes/SF_2024_A_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

>>>>

#### Data wrangling
Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:

{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_2024_ACS-Chem-Bio_wrangling.R dname="F_2024_ACS-Chem-Bio_wrangling">}}

### 2025-08-29 StudyInformation_includes/SF_2024_B_include.qmd
Fixed the SF 2024 data pages to include wrangling scripts and accession numbers
Addressing more of the reviewer comments, accession numbers mostly

##### Journal
ACS Chemical Biology

@@

>>>>

##### Journal
Chemical Communications, Issue 52, 2024

@@

#### Data wrangling
Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:

{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_2024_ChemComm_wrangling.R dname="SF_2024_ChemComm_wrangling">}}

### 2025-08-29 StudyInformation_includes/SK_2024_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

>>>>

#### Data wrangling
Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:

{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SK_2024_wrangling.R dname="SK_2024_wrangling">}}

### 2025-08-29 StudyInformation_includes/WY_2021_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

>>>>

#### Data wrangling
Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:

{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/WY_2021_wrangling.R dname="WY_2021_wrangling">}}
